JLyrics \titlenote{Submitted as the final project for CS 410 Summer 2014.}

### 2014-08-02 report/paper.tex
Updated the piapro section a bit.

\documentclass{acm} % this finds the file "acm.bst"
\usepackage{easyfig}
\usepackage[utf8]{inputenc}
\usepackage{CJK,CJKspace,CJKpunct}
\usepackage{cite,graphicx}

@@

\easyfigdefault{placement={!htb}, max width=20pc, max height=.5\textheight, keepaspectratio}

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. An example screenshot of Rocket Player showing a song's lyrics is in Figure~\ref{fig:res/rocket-player.png}. This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

\Figure[caption={Rocket Player Displaying Song Lyrics}, max height=.3\textheight]{res/rocket-player.png}

Finally, if someone finds a song they like, there is a good chance that the song's producer has made other likable songs. Our search engine would be one more avenue for users to find new material to enjoy themselves with.

@@

Piapro was a fairly simple site to crawl due to the site's structure. The pages were all indexed by number, which could be accessed via changing the URL itself. The first page could be accessed at \url{http://piapro.jp/text/?categoryId=7\&page=1}. Changing the URL page number past the last page returns a page that says ``見つかりませんでした。'' or ``Couldn't find it.'' Each of these pages lists ten songs, for a grand total of just over 47,000 songs. These links are stored under \url{http://piapro.jp/t/} on the site itself. Each song has a unique id of four characters, such as ``KlF-'', which goes after the previous url. These pages contain the title, author, and lyrics data we needed.

@@

\begin{enumerate}
 \item (?<=/t/).\{4\} : Used to match song links because all songs had a four character id under the /t/ directory.
 \item (?<=「).*(?=」) : Used to match the title on the song page, since they were contained in the square open quote.
 \item (?<=\"/).*?(?=\" class=\"i\_icon) : Used to match the user name, since it always followed the tag with i\_icon in it.
 \item p id=\"\_txt\_main\" : Used to find the first line of lyrics, which had a different pattern in the html document.
 \item (?<=>).*(?=<br) : Used to match the first line of lyrics
 \item \^.+(?=<br) : Used to match all other lyrics, each of which had a line break tag after it.
 \item \^.*(?=</p) : Used to match the last line of lyrics, which breaks out of the processing loop.
\end{enumerate}

@@

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used:

\begin{enumerate}
 \item Pages 1-69,999: Zach's laptop
 \item Pages 70,000-79,999: Zach's laptop via ssh to EWS
 \item Pages 80,000-99,999: EWS machine no. 1
 \item Pages 100,000-141,357: EWS machine no. 2
\end{enumerate}

@@

\Figure[caption=Search Failure With cmd.exe]{res/cmd_search_fail.png}

@@

\Figure[caption=Search Success With PuTTY]{res/putty_search_success.png}

>>>>

\documentclass{acm} % this finds the file "acm.bst"
\usepackage{easyfig}
\usepackage[utf8]{inputenc}
\usepackage{CJK,CJKspace,CJKpunct}
\usepackage{cite,graphicx}
% \usepackage[T1]{fontenc}

@@

\easyfigdefault{placement={!htb}, max width=20pc, max height=\textheight, keepaspectratio}

@@

Secondly, finding information on the song itself can assist the listener in learning foreign languages. Repetition is the best methods for learning. Listening to enjoyable music and recognizing new words each time the song is played is a fun way to strengthen one's language capabilities through repetition. Many music players such as foobar2000 and Rocket Player will display the lyrics of a song that is being played so long as those lyrics have been embedded into the music file as a tag. An example screenshot of Rocket Player showing a song's lyrics is in Figure~\ref{fig:res/rocket-player.png} This feature can be used in tandem with the learner's interest in following along with the song to promote learning the language. If one is clever, they could put the same lyrics into the karaoke variant of the song and practice singing to improve their reading and speaking abilities. Regardless of the reason, they user would need to find the full lyrics from the song. We want to help with this cause.

\Figure[caption="Rocket Player Displaying Song Lyrics]{res/rocket-player.png}

Finally, if someone finds a song they like, there is a good chance that the songs made by that song's producer would also be likable.

@@

Piapro was a fairly simple site to crawl due to the site's structure. The pages were all indexed by number, which could be accessed via changing the URL itself. The first page could be accessed at \url{http://piapro.jp/text/?categoryId=7\&page=1}. Changing the URL page number past the last page returns a page that says ``見つかりませんでした。'' or ``Couldn't find it.'' Each of these 4710 pages lists thirty songs, for a grand total of just over 141,000 songs. These links are stored under \url{http://piapro.jp/t/} on the site itself. Each song has a unique id of four characters, such as ``KlF-'', which goes after the previous url. These pages contain the title, author, and lyrics data we needed.

@@

\begin{enumerate}
 \item (?<=/t/).\{4\} : Used to match song links because all songs had a four character id under the /t/ directory.
 \item (?<=「).*(?=」) : Used to match the title on the song page, since they were contained in the square open quote.
 \item (?<=$''$/).*?(?=$''$ class=$''$i\_icon) : Used to match the user name, since it always followed the tag with i\_icon in it.
 \item p id=$''$\_txt\_main$''$ : Used to find the first line of lyrics, which had a different pattern in the html document.
 \item (?<=>).*(?=<br) : Used to match the first line of lyrics
 \item \^{}.+(?=<br) : Used to match all other lyrics, each of which had a line break tag after it.
 \item \^{}.*(?=</p) : Used to match the last line of lyrics, which breaks out of the processing loop.
\end{enumerate}

@@

Due to the sheer number of songs to crawl, it became necessary to distribute the processing over a number of computers. Another issue was that EWS lacks the required libraries to compile this code or even run the executable. As a result, a simplification needed to be made. This time, the crawler simply took the html files, so that they could all be processed on a machine with the required library files. In short, the original crawler was split into two parts. As a result, the following scheme was used: (Note: Actual number of docs ended up being 141,303, but due to the site being updated, there were duplicate links.)

\begin{itemize}
 \item Links 1-69,999: Zach's laptop
 \item Links 70,000-79,999: Zach's laptop via ssh to EWS
 \item Links 80,000-99,999: EWS machine no. 1
 \item Links 100,000-141,357: EWS machine no. 2
 \item Total curl commands required: 146,067
\end{itemize}

@@

\Figure[caption="cmd.exe on Windows Failure"]{res/cmd_search_fail.png}

@@

\Figure[caption="PuTTY on Windows Success"]{res/putty_search_success.png}
